Progress with the NOSAMS

### 2021-05-02 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Minor fixes

- Skip a time-consuming reduction to graphite
- Eliminate blank associated with graphitization

@@

.pull-left[
### Conditions
* Modern and dead CO<sub>2</sub>
* 8m x 50 μm capillary
* 0-4 atm supply pressure

@@

Gas mixtures - helium dilution:
* Increase pressure and total flow
* Reduce pCO<sub>2</sub>
* CO<sub>2</sub> flow remains constant? No - viscosity
]

@@

<br>
### $$PV=nRT$$

@@

@@

@@

* Pre-sputter target
* Displace sample from vial to split with He 
* Measure ratios for 15-30 min.
]

.pull-right[
.center[![gilson autosampler](images/gilson.png)]
.right[Automated gas handling system]
]

@@

* Note similarity to first tests
* Flat top means stable currents/ratios for long enough to measure
* Sample size can be reduced to 2 mL
* Further reduction with increased flow to source

@@

.pull-right[
<br>
<br>
<br>
```{r cur-flow-os, fig.height=6, dev='svg'}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 3, color = "#0069b1") +
  labs(title = "Vial dillution current",
       subtitle = "250μL/min displacement, 30μl/min delivery",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

$$I_{sample} + I_{blank} = I_{meas}$$
$$Fm_m=Fm_bI_b+Fm_sI_s$$

@@

```{r blank-model, fig.height = 4, dev='svg'}
# Plot of data and model with measured blanks
ggplot(ds, aes(Cur_inv, mean, color = Gas)) +
  geom_abline(slope = blankfit$LiveGas_Cur_inv, 
              intercept = blankfit$`LiveGas_(Intercept)`,
              color = "#0069b1") +
  geom_abline(slope = blankfit$DeadGas_Cur_inv, 
              intercept = blankfit$`DeadGas_(Intercept)`,
              color = "#00a9e0") +
  geom_pointrange(aes(ymin = mean - merr, ymax = mean + merr), size = .3) + 
  scale_color_manual("Gas", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  xlim(0, 10) +
  labs(title = "Modelled blank",
       subtitle = "Fits cross at Fm and current of blank",
       x = "Inverse 12C Current (μA-1)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = "none",
        legend.background = element_rect(fill = "white", color = "black"))

factor(ds$Gas)
```
]

@@

Karl von Reden, Ann McNichol

@@

# Sample size reduction

Open split defines pressure, therefore

smaller samples = higher dilution = higher flow

plot: sample size vs. required flow

pressure control to maintain constant CO<sub>2</sub> to source

figure: setup with pressure control

>>>>

- Skip a time-consuming reduction to graphite
- Rapid iteration for science/development
- Eliminate blank associated with graphitization

@@

.pull-left[
### Conditions
* Pure CO<sub>2</sub> to source
* Modern and dead CO<sub>2</sub>
* 8 m x 50 μm capillary
* 0-4 atm supply pressure

@@

Gas mixtures - helium dilution:
* Increase pressure and total flow
* Reduce pCO<sub>2</sub>
* CO<sub>2</sub> flow remains constant? No - viscosity
* He is 25% more viscous than CO<sub>2</sub>
]

@@

### $$PV=nRT$$

@@

### $$Q=\frac{\Delta P \pi R^4}{8\mu L}$$
]

@@

1/viscosity = flow

@@

* Pre-sputter target
* Displace sample from vial to split with He 
* Measure ratios for 15-30 min.

.pull-right[
.center[![gilson autosampler](images/gilson.png)]
.right[Automated gas handling system (Roberts, 2013)
]
]

@@

* Note similarity to first tests
* Flat top means stable currents/ratios for long enough to measure
* Sample size can be reduced to 2 mL (~1 mg C)
* Further reduction with increased flow to source

@@

.pull-right[
<br>
<br>
<br>
```{r cur-flow-os, fig.height=6, dev='svg'}
ggplot(data, aes(co2flow, he12C)) +
  geom_smooth(span = .3, se=FALSE, color = "#00b7bd") +
  geom_point(size = 3, color = "#0069b1") +
  labs(title = "Vial dilution current",
       subtitle = "250μL/min displacement, 30μl/min delivery",
       x = bquote('CO'[2]~'Flow (μl/min)'), 
       y = "12C current (μA)") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff")
```
]

@@

$$I_{sample} + I_{blank} = I_{meas}$$
$$Fm_mI_m=Fm_bI_b+Fm_sI_s$$

@@

```{r blank-model, fig.height = 4, dev='svg'}
# Plot of data and model with measured blanks
ggplot(ds, aes(Cur_inv, mean, color = Gas)) +
  geom_abline(slope = blankfit$LiveGas_Cur_inv, 
              intercept = blankfit$`LiveGas_(Intercept)`,
              color = "#0069b1") +
  geom_abline(slope = blankfit$DeadGas_Cur_inv, 
              intercept = blankfit$`DeadGas_(Intercept)`,
              color = "#00a9e0") +
  geom_pointrange(aes(ymin = mean - merr, ymax = mean + merr), size = .3) + 
  scale_color_manual("Gas", values = c("#b7bf10", "#00a9e0", "#0069b1")) +
  xlim(0, 10) +
  labs(title = "Modeled blank",
       subtitle = "Fits cross at Fm and current of blank",
       x = "Inverse 12C Current (μA-1)",
       y = "Fraction modern") +
  theme_classic() +
  theme_xaringan(title_font_size = 20,
                 text_font_size = 16,
                 background_color = "#ffffff") +
  theme(legend.position = "none",
        legend.background = element_rect(fill = "white", color = "black")) 
```
]

@@

Karl von Reden

@@
